---
title: "Project1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  fig.path='Figs/')
```
Save the data in tempfile named "act", csv has been saved in the C drive.
Remove the NA rows so that we can ignore them for this part

```{r activity, include=TRUE}
setwd("C:/")

library(ggplot2)
library(dplyr)
library(gridExtra)
act<-read.csv("activity.csv",header=TRUE,sep=",")
actsub<-subset(act, !is.na(act$steps))
df<-as.data.frame(act)
df[is.na(df)]<-0
dfsum<-cbind(aggregate(steps ~ date, df, sum))
dfsum$steps<-dfsum$steps/288
dfsumint<-cbind(aggregate(steps ~ interval, df, sum))
dfsumint$steps<-dfsumint$steps/53
```

Histogram of Steps

```{r histogram, echo=TRUE}

hist(actsub$steps,main="",xlab="Steps")
```

Average Number of Steps, [NA] values removed

```{r steps.avg, echo=TRUE}
mean(actsub$steps)
```

Median Number of Steps, [NA] values removed

```{r steps.median, echo=TRUE}
median(actsub$steps)
```

Time-Series Plot

```{r time series, echo=TRUE}

ggplot(dfsumint, aes(interval, steps)) + geom_line() + ylab("Avg Steps")

```

The Maximum Average Number of Steps Occured at Interval

```{r maxavg, echo=TRUE}
findmax<-head(arrange(dfsumint, desc(steps)))
maxint<-first(findmax$interval)
maxint
```
Number of NA Values in the File:
```{r Handle NA values,echo=TRUE}
sum(is.na(act))
```
Replace NA Values with Average over Day:
```{r handle NA, echo=TRUE}
dfsum$steps<-dfsum$steps/288
NAs.a <- is.na(act$steps)
act$steps[NAs.a] <- dfsum[match(act$date[NAs.a], dfsum$date),]$steps

```

```{r histimput, echo=TRUE}

hist(act$steps,main="",xlab="Steps")
```

Average Number of Steps, [NA] values imputed

```{r imputed.avg, echo=TRUE}
mean(act$steps)
```

Median Number of Steps, [NA] values imputed

```{r imputed.median, echo=TRUE}
median(act$steps)
```

We do not see much of a difference when we impute the values using the average over the day.

Add a Variable Telling us Whether the Date is a Weekend or Weekday and then Plot Time-Series of the Intervals on Weekends and Weekdays

``` {r WeekendWeekday, echo=TRUE}
act$weekday=ifelse(weekdays(as.Date(act$date)) %in% c("Saturday","Sunday"),"Weekend","Weekday")
actweekend<-act[ which(act$weekday=='Weekend'), ]
actweekday<-act[ which(act$weekday=='Weekday'), ]
actsumintday<-cbind(aggregate(steps ~ interval, actweekday, sum))
actsumintday$steps<-actsumintday$steps/53
actsumintend<-cbind(aggregate(steps ~ interval, actweekend, sum))
actsumintend$steps<-actsumintend$steps/53
p1<-ggplot(actsumintday, aes(interval, steps)) + geom_line() + ylab("Avg Steps") + labs(title="weekday")
p2<-ggplot(actsumintend, aes(interval, steps)) + geom_line() + ylab("Avg Steps") + labs(title="weekend")
grid.arrange(p1,p2,nrow=2)
```

